\documentclass{article}
\usepackage{amsmath, amssymb, verbatim, hyperref}
\author{Patrick Foley and Sam Ventura}
\title{The Effect of Fatigue on Team and Player Performance in Basketball and Hockey}

\begin{document}

\maketitle{}

Many researchers have successfully employed (regularized) logistic regression of points scored on player participation to develop reliable estimates of players’ net contributions to a game.  In some sports, certain players may have valuable skills that can contribute to a team’s success, but are ordinarily unneeded.  Players can base their careers off of very specific skills, sometimes only participating in games to defend against specific threats.  These skills, valued by teams, may not be correctly estimated (or reflected at all) in models based entirely on points scored.

We propose estimating player skills by regressing game events against player participation.  A logistic regression of an assisted two-point shot attempt by an opposing team’s center or power forward against the participation of the other team’s point guard, for example, might reveal which guards excel at preventing low post entry passes.  Estimates of these basketball skills may be valuable to managers with good teams missing specific pieces.  

We successfully identify role players who excel at very specific skills, but do not otherwise show strong net contributions to their team’s success.  In many notable cases, our estimates agree with common media descriptions of player’s roles.  


\end{document}
